Optimal (Multiway) Spatial Joins

### 2024-05-25 msj.tex
yufei

Next, we construct from $H'$ a new set of horizontal segments: 
\myeqn{
    H^* = \set{h^* \mid h' \in H' \text{ and its minimal segment $h^*$ exists}}. \label{eqn:hv:type2:H*}
}
Computing $H^*$ from $H'$ and $V$ is an instance of Problem $\mathscr{B}$, and can be achieved in $O(n \log n)$ as per the discussion from Section~\ref{sec:bricks}.

@@

\extraspacing {\bf Computing the Top-Sliced Rectangles.}

@@

>>>>

Next, we construct a new set of horizontal segments: 
\myeqn{
    H^* = \set{h^* \mid h' \in H' \text{ and its minimal segment $h^*$ exists}}. \label{eqn:hv:type2:H*}
}
This can be done in $O(n + k \cdot \out)$ time, as shown in Appendix~\ref{app:hv}.

%Computing $H^*$ from $H'$ and $V$ is an instance of Problem $\mathscr{B}$, and can be achieved in $O(n \log n)$ as per the discussion from Section~\ref{sec:bricks}.

@@

\extraspacing {\bf Computing $\bm{R^*_1, R^*_2, ..., R^*_{k-2}}$.}

@@

\extraspacing {\bf Computing $\bm{H^*}$.}
